Describing the C-space of asynchronous periodic task using DIT

### 2013-07-26 dit-paper_ieee.tex
corrected reference to the Wolsey book

			As explained in \cite{wolsey2000integer}, a region of $\mathbb{N}_0^n$ such as the C-space can be described by a \emph{polytope}, or a list of parametric linear constraints (called the \emph{formulation}). The constraints must be conditions which can unequivocally decide if a point is included in the region or not. In the sequel we give a formulation for the C-space in $\mathbb{N}_0^n$\footnote{For a formulation in $\mathbb{N}^n$ rather than in $\mathbb{N}_0^n$, the following inequations can be added to the formulation \[ C_i \geqslant 1 \; \forall i \]}.\\

>>>>

			As explained in \cite{nemhauser1988integer}, a region of $\mathbb{N}_0^n$ such as the C-space can be described by a \emph{polytope}, or a list of parametric linear constraints (called the \emph{formulation}). The constraints must be conditions which can unequivocally decide if a point is included in the region or not. In the sequel we give a formulation for the C-space in $\mathbb{N}_0^n$\footnote{For a formulation in $\mathbb{N}^n$ rather than in $\mathbb{N}_0^n$, the following inequations can be added to the formulation \[ C_i \geqslant 1 \; \forall i \]}.\\
